paper

### 2024-09-25 inst/extdata/paperdata/paper.qmd
proteogenomics

```{r}
# Load necessary packages
library(LimROTS)
library(parallel)
# Load the dataset
data("Columbia.RealCase")
print(Columbia.RealCase)

@@

data.assay <- assay(Columbia.RealCase)
data.assay <- preprocessCore::normalize.quantiles(as.matrix(data.assay))

# Set metadata and formula for LimROTS analysis
meta.info <- c("groups" , "Age" , "gender" , "LRRK2.status" , "GBA.status")
B <- 1000  # Number of bootstrap samples
K <- dim(Columbia.RealCase)[1]/4  # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 10  # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "groups"
formula.str <- "~ 0 + groups + Age + gender + LRRK2.status + GBA.status"  # Formula for group comparison
# Run LimROTS analysis with trend and robust settings enabled

trace(LimROTS, edit = T)

limrots.result <- LimROTS(data.exp = Columbia.RealCase, 
                          B = B, K = K, meta.info = meta.info, 
                          cluster = cluster, group.name = group.name, 
                          formula.str = formula.str, trend = TRUE, robust = TRUE, progress = TRUE, seed.cl = 1234)

saveRDS(limrots.result, "inst/extdata/paperdata/Columbia.RealCase.LimROTS.rds")
```

@@

```{r}
library(ggplot2)
# Create a data frame from the LimROTS results
limrots.result.df <- data.frame(proteins = row.names(limrots.result$data),
                                LimROTS.FC = limrots.result$logfc,
                                q.value = limrots.result$q_values$pvalues)

# Create a volcano plot
ggplot(limrots.result.df, aes(x = limrots.result$corrected.logfc, y = -log10(limrots.result$q_values$qvalues) )) +
  geom_point(alpha = 0.8) +
  theme_bw() +
  labs(title = "Volcano Plot", x = "Log Fold Change", y = "-Log10 q.value", color = "True Positive") +
  scale_color_manual(values = c("grey", "red"))+
  geom_hline(yintercept=-log10(0.05), linetype="dashed", color = "blue")+
  geom_hline(yintercept=-log10(0.01), linetype="dashed", color = "black") 
```

>>>>

```{r}
# Load necessary packages
library(LimROTS)
library(parallel)
# Load the dataset
load("D:\\MJFF\\MJFF V2 10.30.2023\\proteogenomic study\\soma.rda")
print(soma)

@@

# Set metadata and formula for LimROTS analysis
meta.info <- c("group_comp" , "gender" , "AGE") 
B <- 1000  # Number of bootstrap samples
K <- dim(soma)[1]/4  # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 10  # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "group_comp"
formula.str <- "~ 0 + group_comp + gender + AGE"  # Formula for group comparison
# Run LimROTS analysis with trend and robust settings enabled

limrots.result <- LimROTS(data.exp = soma, 
                          B = B, K = K, meta.info = meta.info, 
                          cluster = cluster, group.name = group.name, 
                          formula.str = formula.str, trend = TRUE, robust = TRUE, progress = TRUE, seed.cl = 1234)

saveRDS(limrots.result, "inst/extdata/paperdata/soma.LimROTS.rds")
```

@@

```{r}
library(ggplot2)
# Create a data frame from the LimROTS results
limrots.result.df <- data.frame(proteins = row.names(limrots.result$data),
                                LimROTS.FC = limrots.result$corrected.logfc,
                                p.value = limrots.result$q_values$pvalues)

# Create a volcano plot
ggplot(limrots.result.df, aes(x = LimROTS.FC, y = -log10(p.value) )) +
  geom_point(alpha = 0.8) +
  theme_bw() +
  labs(title = "Volcano Plot", x = "Log Fold Change", y = "-Log10 q.value", color = "True Positive") +
  scale_color_manual(values = c("grey", "red"))+
  geom_hline(yintercept=-log10(0.05), linetype="dashed", color = "blue")+
  geom_hline(yintercept=-log10(0.01), linetype="dashed", color = "black") 
```

```{r}
library(SomaScan.db)
soma@NAMES

select(SomaScan.db, keys = "9073-35", columns = c("SYMBOL", "UNIPROT"))
